Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2023-11-20 manuscript/manuscript.qmd
Minor typos

To judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions. Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner [@Sloan:2009; @GordonKnockNeely:2009]

@@

```{r}
#| label: fig-transp-acc
#| fig-width: 6
#| fig-height: 2.5
#| out-width: "80%"
#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability"
#| include: true
mms_trans_acc_all <- mms_transp_acc %>% 
  filter(
    (feat_transp == "Transparency: Yes" & feat_acc == "Accountability: Yes") | 
      (feat_transp == "Transparency: No" & feat_acc == "Accountability: No")) %>% 
  bind_rows(
    mms_transp %>% 
      filter(feature_level == "Transparency: Yes") %>% 
      rename(feat_transp = feature_level) %>% 
      mutate(feat_acc = "Accountability: No"),
    mms_acc %>% 
      filter(feature_level == "Accountability: Yes") %>% 
      rename(feat_acc = feature_level) %>% 
      mutate(feat_transp = "Transparency: No")
  )

@@

To calculate the marginal mean for a feature, we find the average predicted value across each the levels of that feature. To illustrate, assume that @apptbl-grid-example represents the full reference grid of all experimental features and levels. The marginal means for transparency would be (`r p_sm$transparency_no$list`)/3 = `r p_sm$transparency_no$emm` when transparency is set to "no", and (`r p_sm$transparency_yes$list`)/3 = `r p_sm$transparency_yes$emm` when transparency is set to "yes". In reality, the marginal mean for transparency reported in @fig-all-results and @apptbl-all-results represent the average of 288 rows where transparency is no and 288 rows where transparency is yes.

>>>>

To judge organizational accountability, donors may use ratings by watchdog organizations like Charity Navigator and GuideStar as heuristics to guide their decisions. Research shows that initiatives to address accountability gaps by these organizations can affect donations to organizations in a significant manner [@Sloan:2009; @GordonKnockNeely:2009].

@@

```{r}
#| label: fig-transp-acc
#| fig-width: 6
#| fig-height: 2.5
#| out-width: "80%"
#| fig-cap: "Estimated marginal means for the four combinations of transparency and accountability."
#| include: true
mms_trans_acc_all <- mms_transp_acc %>% 
  filter(
    (feat_transp == "Transparency: Yes" & feat_acc == "Accountability: Yes") | 
      (feat_transp == "Transparency: No" & feat_acc == "Accountability: No")) %>% 
  bind_rows(
    mms_transp %>% 
      filter(feature_level == "Transparency: Yes") %>% 
      rename(feat_transp = feature_level) %>% 
      mutate(feat_acc = "Accountability: No"),
    mms_acc %>% 
      filter(feature_level == "Accountability: Yes") %>% 
      rename(feat_acc = feature_level) %>% 
      mutate(feat_transp = "Transparency: No")
  )

@@

To calculate the marginal mean for a feature, we find the average predicted value across each the levels of that feature. To illustrate, assume that @apptbl-grid-example represents the full reference grid of all experimental features and levels. The marginal means for transparency would be (`r p_sm$transparency_no$list`)/3 = `r p_sm$transparency_no$emm` when transparency is set to "no", and (`r p_sm$transparency_yes$list`)/3 = `r p_sm$transparency_yes$emm` when transparency is set to "yes". In reality, the marginal mean for transparency reported in @fig-all-results and @apptbl-all-results reflects the average of 288 rows where transparency is no and 288 rows where transparency is yes.
